Automatic Visual Inference for Linear Regression

### 2022-03-16 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
lack conclusion and future

# $p$-value

@@

.caption[
Fig. 10: _Quasibinomial GLM fitted for estimated power for different number of evaluations. The left plot is for the cubic model, the right plot is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

.caption[
Fig. 11: _Binomial GLM fitted for rejection for different number of evaluations. The left plot is for the cubic model, the right plot is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

# Performance

>>>>

# $p$-value of Lineup Protocol

@@

.caption[
Fig. 10: _Quasibinomial GLM fitted for estimated power for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

.caption[
Fig. 11: _Binomial GLM fitted for rejection for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

.center[![:scale 80%](images/system_pow_1.png)

.caption[
Fig. 16: _Power of the automatic visual test compared to human visual test. The blue curve is the power of the automatic visual test. The dashed line represents the power of the conventional test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity._ 
]]

.center[![:scale 80%](images/system_pow_2.png)

.caption[
Fig. 17: _Power of the automatic visual test with different number of evaluations. The dashed line represents the power of the conventional test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity._ 
]]
